Inferring Continuous and Discrete Population Genetic Structure Across Space

### 2017-09-12 writeup/conStruct.tex
changes to appendix

We thank Marjorie Weber, Yaniv Brandvain, William Wetzel, 
Mariah Meek, Doc Edge, and Matthew Stephens 
for invaluable comments on the method and manuscript, 
as well as Quentin Cronk, who provided input on the \textit{Populus} analyses, 
and Emily Puckett, who provided input on the black bear analyses.
We also thank the attendees at the 2017 SSE Meeting in Portland, OR, 
whose votes determined the name of the method.
This work was supported in part by 
the National Science Foundation under award number NSF \#1262645 (DBI) to PR and GC, 
the National Institute of General Medical Sciences of the National Institutes of Health under award numbers NIH RO1GM83098 and RO1GM107374 to GC,
and the National Science Foundation under award numbers NSF \# 1148897 and \# 1402725 to GB.

@@

\section{Model rationale}
\subsection{Drift, admixture, and space} \label{rationale}
\paragraph{Drift} 
We first provide a simple model of allele frequencies within a cluster. 
Imagine a sample $i$ that draws all of its ancestry from cluster $k$.
The allele frequency in sample $i$ at locus $\ell$, $F_{i,\ell}$ can be
written as the sum
\begin{equation}
F_{i,\ell} = \epsilon_{\ell} + \Delta^{(k)}_{\ell} +
\Delta^{(k,i)}_{\ell} + \Delta^{(i)}_{\ell}
\label{drift_terms_no_admix}
\end{equation}
The first term is the ancestral allele frequency $\epsilon_\ell$ shared by all samples; 
the second is the deviation from that ancestral frequency 
due to drift in the ancestral population of the $k$th cluster,
which is shared by all samples within the cluster. 
The third term is the deviation of the $i$th sample away from the $k$th cluster mean 
due to the spatial process of drift and migration within the cluster.
The final term is the deviation specific to the $i$th sample,
which captures drift not shared by all samples at the population level
(i.e., subpopulation-specific drift due to, e.g., inbreeding). 
We will assume that these four deviations are all uncorrelated with each other.

If we have two samples $i$ and $j$ drawn from cluster $k$, 
their covariance across loci will be 
\begin{equation}
\text{Var}(\epsilon) +  \text{Var}\left( \Delta^{(k)} \right) +
\text{Cov}(\Delta^{(k,i)}_{\ell},\Delta^{(k,j)}_{\ell}) + \delta_{i=j} \text{Var}\left( \Delta^{(i)} \right)\ \\
\end{equation}
where the quantity $\delta_{i=j}$ is an indicator variable that equals 1 when $i$ is equal to $j$ and 0 otherwise, 
as in Eqn. \eqref{cross_cluster_covariance}.

\paragraph{Admixture} 
The model above describes the simple case 
in which samples draw 100\% of their ancestry from only a single cluster each. 
To accommodate admixture between clusters, 
we model allele frequencies within samples as linear combinations of the population-specific 
drift terms across the clusters from which they draw ancestry.
To do so, we introduce a term $w^{(k)}_{i}$ that describes the
admixture proportion of sample $i$ in cluster $k$ ($\sum_{K}w^{(k)}_{i} = 1$),
which can be interpreted as the proportion of the genome in the $i$th
sample that came from the $k$th cluster 
(or the probability that an allele at a locus is drawn from $k$).
The allele frequency in the $i$th sample at the $\ell$th locus can therefore be written as:
\begin{equation}
F_{i,\ell} = \epsilon_{\ell} + \sum\limits_{K} w^{(k)}_{i}\left( 
  \Delta^{(k)}_{\ell} + \Delta^{(k,i)}_{\ell}\right) + \Delta^{(i)}_{\ell}	
\label{drift_terms_admix}
\end{equation}
and the covariance between $i$ and $j$ across loci is
\begin{equation}
\Omega_{i,j} = \text{Var}(\epsilon) + \sum\limits_K w^{(k)}_iw^{(k)}_j
\left(
  \text{Var}\left( \Delta^{(k)} \right) +
\text{Cov}(\Delta^{(k,i)}_{\ell},\Delta^{(k,j)}_{\ell}) 	\right) +
\delta_{i=j} \text{Var}(\Delta_i)
\label{admixed_spatial_cov}
\end{equation}

@@

\section{Allelic Covariance}\label{allelic_cov}
To see how to arrive at Eqn. \eqref{allelic_covariance},
pick a random locus and
let $A$ and $B$ be randomly drawn alleles at that locus from populations $i$ and $j$ respectively.
If $i=j$, then these are chosen \emph{without} replacement.
Suppose these are each coded as `0' or `1` (where `0' denotes a reference allele),
but we randomly ``flip'' this coding, so that we let $X=A$ and $Y=B$ with probability 1/2,
but otherwise we let $X=1-A$ and $Y=1-B$.
We then let $\widehat{\Omega}_{i,j} = \cov[X,Y]$ ; 
sampling without replacement makes the statistic insensitive to sample size,
and random allele flipping makes it independent of the choice of reference allele.
By conditioning on the flip,
and using the fact that $\E[X] = \E[Y] = 1/2$,
Eqn. \eqref{allelic_covariance} comes from the calculation that
\begin{align}
\cov[X,Y] &= \E[XY] - 1/4 = (1/2)\E[AB + (1-A)(1-B)] - 1/4\\\notag
&= \E[(A-1/2)(B-1/2)]
\end{align}
The factor of $\delta_{i,j}/(N_i-1)$ comes from the fact that if $i=j$,
then $\E[AB]$ is the probability that both alleles drawn without replacement are reference,
which is $f_i^2 n/(n-1)$.
\paragraph{Likelihood}
If our allele frequency deviations are well approximated by a Gaussian, 
their sample allelic covariance is a sufficient statistic,
so that calculating the likelihood of their sample allelic covariance is the same as 
calculating the probability of the frequency data up to a constant. 
We can therefore model the covariance of the sample allele frequencies, $\widehat{\Omega}$, 
as a draw from a Wishart distribution with degrees of freedom equal to 
the number of loci $L$ across which the sample allelic covariance is calculated:
\begin{equation}
\widehat{\Omega} \sim \mathcal{W}\left( L\Omega, L	\right)
\label{wishart}
\end{equation}

@@

\newpage
\section{Cross validation}\label{Xvalidation}
To perform model comparison, we employ a Monte Carlo cross-validation approach \citep{picard1984}.
This cross-validation procedure generates a mean predictive accuracy for each model and each value of $K$, 
as well as a confidence interval around that mean,
which can then be used for model comparison or selection.
Briefly, we follow the following procedure:
\begin{enumerate}
\item For each of $X$ replicates:
	\begin{enumerate}
		\item partition the allele frequency data into a 90\% ``training'' partition ($F^x_1$) and a 10 \%``testing" partition ($F^x_2$) \label{partition}
		\item run our inference procedure on the training partition to estimate model parameters $\theta_{mk}$ for: \label{inference}
			\begin{enumerate}
				\item $m$: the spatial and the nonspatial model
				\item $k$: the number of clusters 1 through $K$
			\end{enumerate}	
	\item calculate the mean log likelihood of the testing data partition, 
	over the posterior distribution of training-estimated parameters for each model 
	($\bar{\mathcal{L}}(F^x_2 \mid \theta_{mk})$, henceforth $\bar{\mathcal{L}}_{xmk}$) \label{lnL}
	\item generate standardized mean log likelihoods, $\mathcal{Z}_{xmk}$, across models: \label{standardize}
		\begin{enumerate}
			\item identify the highest mean log likelihood, $\bar{\mathcal{L}}^\text{max}_{xmk}$
			\item subtract $\bar{\mathcal{L}}^\text{max}_{xmk}$ from $\bar{\mathcal{L}}_{xmk}$ across all models,
				such that the standardized log likelihood, $\mathcal{Z}_{xmk}$, of the best model is 0,
				and less than 0 for all inferior models. 
		\end{enumerate}
	\end{enumerate}
\item For each model (i.e., each combination of $m$ and $k$) calculate 
	the mean standardized log likelihood of the testing data partition across $X$ replicates, 
	as well its standard error and 95\% confidence interval:
	\begin{enumerate}
	\item mean
		\begin{equation}
			\bar{\mathcal{Z}}_{mk} = \frac{1}{X}\sum\limits_{x=1}^{X}\mathcal{Z}_{xmk}
		\end{equation}
	\item standard error
		\begin{equation}
			SE_{\bar{\mathcal{Z}}_{mk}} = \sqrt{\frac{\sum\limits_{x=1}^{X} \left[ {\mathcal{Z}_{xmk} - \bar{\mathcal{Z}}_{mk}} \right]}{X}}
		\end{equation}
	\item 95\% confidence interval
		\begin{equation}
			95\% \text{CI} = \bar{\mathcal{Z}}_{mk} \pm 1.96 \times SE_{\bar{\mathcal{Z}}_{mk}}
		\end{equation}
	\end{enumerate}
\end{enumerate}

\newpage
\section{Calculating layer importance}\label{layer_importance}
First, we describe the allelic covariance between two samples, $i$, and $j$.
Note that this is the allelic covariance described in Eqn \eqref{allelic_covariance},
in which we randomly polarize alleles,
and not the genetic covariance, which subtracts mean allele frequencies.
Let $A$ and $B$ be a randomly chosen alleles from the two samples, respectively,
at a randomly chosen locus 
(if the two populations are the same, then choose without replacement).
Then, if we let $X=2(A-1/2)$ and $Y=2(B-1/2)$,
since $X$ and $Y$ take the values $\pm 1$,
and thanks to the random polarization, $\E[A] = \E[A] = 1/2$,
$$\begin{aligned}
\E[XY]
        &= \P\{ X=Y \} - \P\{ X \neq Y \} \\
        &= 2 \P\{ X=Y \} - 1 \\
        &= 1 - 2 \P\{ X \neq Y \} .
\end{aligned}$$
To translate, $\P\{ X=Y \}$ is the probability that the alleles from our two focal samples agree with each other,
while $\P\{ X \neq Y \}$ is the probability that they disagree.
For the first thing to happen, $i$ and $j$ must coalesce before coalescing with the reference samples,
so for $X$ and $Y$ to agree they must be more closely related than typical in the population.
The last part, $\P\{ XY \neq 0\}$, is the probability that both samples disagree from the references.
(This implies that $\E[XY] = 1 - 2 D_{ij}$, 
where $D_{ij}$ is the probability that two randomly chosen alleles differ, 
which is the genetic divergence.)

Now, here is a generative model that gives us the form of the covariance we have postulated.
To decide whether or not $X$ and $Y$ will agree,
first each sample randomly chooses a layer: call these $I$ and $J$.
The probability that $X$ chooses layer $k$ is $\P{I=k}$, which is $w_i^{(k)}$, 
the $i$th sample's admixture proportion in the $k$th layer.
The same holds true for $Y$.
If they do not choose the same layer, the probability that they agree is $p_\gamma$.
If they do choose the same layer, 
then they agree with a probability $p_\gamma + q^{(k)}_{ij}$ that depends on their distance apart.
Here

@@

One way to summarize the contribution of each layer is to partition the probability of agreement
into contributions due to agreement ``in" each layer.
So, the contribution from layer $k$ to agreement between $i$ and $j$ is 
$w_i^{(k)} w_j^{(k)} q^{(k)}_{ij} / (p_\gamma + \sum_K w_i^{(k)} w_j^{(k)} q^{(k)}_{ij})$,
which is the probability, given that they agree, that they agree thanks to layer $k$.
Similarly, the ``background" contribution is $p_\gamma / (p_\gamma + \sum_K w_i^{(k)} w_j^{(k)} q^{(k)}_{ij})$.
Because our signal comes from \emph{variation} in covariance, we omit the $p_\gamma$ terms.

@@

%
\begin{equation}
\xi^{(k)} = 
	\sum\limits_{i=1}^{N-1}
		\sum\limits_{j=i+1}^N
			w^{(k)}_iw^{(k)}_j 
				\left(	
					2\alpha^{(k)}_0 
						\left( \text{exp} 
							\left( -(\alpha^{(k)}_D D_{i,j}) ^ {\alpha^{(k)}_2}\right) 
						\right) + 2\phi^{(k)} + \frac{1}{2}
				\right)
\label{layer_contribution}
\end{equation}
%
which is that layer's contribution to agreement between samples 
summed over the upper triangle (excluding the diagonal) of the covariance matrix.
We define the importance of the $k$th layer, $\Xi^{(k)}$, 
as the relative contribution of the $k$th layer to total agreement:
%
\begin{equation}
\Xi^{(k)} = 
\frac{\xi^{(k)}}
	{\sum\limits_{k=1}^{K}
	    	\xi^{(k)}}
\label{rel_layer_contribution}
\end{equation}
%

>>>>

We thank Marjorie Weber, Yaniv Brandvain, William Wetzel, 
Mariah Meek, Doc Edge, and Matthew Stephens 
for invaluable comments on the method and manuscript, 
as well as Quentin Cronk, who provided input on the \textit{Populus} analyses, 
and Emily Puckett, who provided input on the black bear analyses.
We also thank the attendees at the 2017 SSE Meeting in Portland, OR, 
whose votes determined the name of the method.
This work was supported in part by 
the National Science Foundation under award number NSF \#1262645 (DBI) to PR and GC, 
the National Institute of General Medical Sciences of the National
Institutes of Health under award numbers NIH R01-GM108779 to GC,
and the National Science Foundation under award numbers NSF \# 1148897 and \# 1402725 to GB.

@@

\section{Model rationale}
\subsection{Drift, admixture, and space} \label{rationale}
\gc{Here we sketch a simple model of allele frequencies and their
covariances, to justify the form given in the main text.}
\paragraph{Drift} 
We first provide a simple model of allele frequencies within a \gc{layer}. 
Imagine a sample $i$ that draws all of its ancestry from cluster $k$.
The allele frequency in sample $i$ at locus $\ell$, $F_{i,\ell}$ can be
written as the sum
\begin{equation}
F_{i,\ell} = \epsilon_{\ell} + \Delta^{(k)}_{\ell} +
\Delta^{(k,i)}_{\ell} + \Delta^{(i)}_{\ell}
\label{drift_terms_no_admix}
\end{equation}
The first term is the ancestral allele frequency $\epsilon_\ell$ shared by all samples; 
the second is the deviation from that ancestral frequency 
due to drift in the ancestral population of the $k$th \gc{layer},
which is shared by all samples within the cluster. 
The third term is the deviation of the $i$th sample away from the
$k$th \gc{layer} mean 
due to the spatial process of drift and migration within the \gc{layer}.
The final term is the deviation specific to the $i$th sample,
which captures drift not shared by all samples at the population level
(i.e., subpopulation-specific drift due to, e.g., inbreeding). 
We will assume that these four deviations are all uncorrelated with each other.

If we have two samples $i$ and $j$ drawn from \gc{layer} $k$, 
their covariance across loci will be 
\begin{equation}
\text{Var}(\epsilon) +  \text{Var}\left( \Delta^{(k)} \right) +
\text{Cov}(\Delta^{(k,i)}_{\ell},\Delta^{(k,j)}_{\ell}) + \delta_{i=j} \text{Var}\left( \Delta^{(i)} \right)\ \\
\end{equation}
where the quantity $\delta_{i=j}$ is an indicator variable that equals 1 when $i$ is equal to $j$ and 0 otherwise, 
as in Eqn. \eqref{cross_cluster_covariance}.

\paragraph{Admixture} 
The model above describes the simple case 
in which samples draw 100\% of their ancestry from only a single \gc{layer} each. 
To accommodate admixture between \gc{layers}, 
we model allele frequencies within samples as linear combinations of the population-specific 
drift terms across the clusters from which they draw ancestry.
To do so, we introduce a term $w^{(k)}_{i}$ that describes the
admixture proportion of sample $i$ in \gc{layer} $k$ ($\sum_{K}w^{(k)}_{i} = 1$),
which can be interpreted as the proportion of the genome in the $i$th
sample that came from the $k$th \gc{layer} 
(or the probability that an allele at a locus is drawn from $k$).
The allele frequency in the $i$th sample at the $\ell$th locus can therefore be written as:
\begin{equation}
F_{i,\ell} = \epsilon_{\ell} + \sum\limits_{K} w^{(k)}_{i}\left( 
  \Delta^{(k)}_{\ell} + \Delta^{(k,i)}_{\ell}\right) + \Delta^{(i)}_{\ell}	
\label{drift_terms_admix}
\end{equation}
and the covariance between $i$ and $j$ across loci is
\begin{equation}
\Omega_{i,j} = \text{Var}(\epsilon) + \sum\limits_K w^{(k)}_iw^{(k)}_j
\left(
  \text{Var}\left( \Delta^{(k)} \right) +
\text{Cov}(\Delta^{(k,i)}_{\ell},\Delta^{(k,j)}_{\ell}) 	\right) +
\delta_{i=j} \text{Var}(\Delta_i)
\label{admixed_spatial_cov}
\end{equation}

@@

\section{Allelic Covariance}\label{allelic_cov}
To see how to arrive at \gc{our empirical variance-covariance expression,} Eqn. \eqref{allelic_covariance},
pick a random locus and
let $A$ and $B$ be randomly drawn alleles at that locus from populations $i$ and $j$ respectively.
If $i=j$, then these are chosen \emph{without} replacement.
Suppose these are each coded as `0' or `1` (where `0' denotes a reference allele),
but we randomly ``flip'' this coding, so that we let $X=A$ and $Y=B$ with probability 1/2,
but otherwise we let $X=1-A$ and $Y=1-B$.
We then let $\widehat{\Omega}_{i,j} = \cov[X,Y]$ ; 
sampling without replacement makes the statistic insensitive to sample size,
and random allele flipping makes it independent of the choice of reference allele.
By conditioning on the flip,
and using the fact that $\E[X] = \E[Y] = 1/2$,
Eqn. \eqref{allelic_covariance} comes from the calculation that
\begin{align}
\cov[X,Y] &= \E[XY] - 1/4 = (1/2)\E[AB + (1-A)(1-B)] - 1/4\\\notag
&= \E[(A-1/2)(B-1/2)]
\end{align}
The factor of $\delta_{i,j}/(N_i-1)$ comes from the fact that if $i=j$,
then $\E[AB]$ is the probability that both alleles drawn without replacement are reference,
which is $f_i^2 n/(n-1)$.
\paragraph{Likelihood}
If our allele frequency deviations are well approximated by a Gaussian, 
their sample allelic covariance is a sufficient statistic,
so that calculating the likelihood of their sample allelic covariance is the same as 
calculating the probability of the frequency data up to a constant. 
We can therefore model the covariance of the sample allele frequencies, $\widehat{\Omega}$, 
as a draw from a Wishart distribution with degrees of freedom equal to 
the number of loci $L$ across which the sample allelic covariance is calculated:
\begin{equation}
\widehat{\Omega} \sim \mathcal{W}\left( L\Omega, L	\right)
\label{wishart}
\end{equation}

@@

\newpage
\section{Cross validation}\label{Xvalidation}
To perform model comparison, we employ a Monte Carlo cross-validation approach \citep{picard1984}.
This cross-validation procedure generates a mean predictive accuracy for each model and each value of $K$, 
as well as a confidence interval around that mean,
which can then be used for model comparison or selection.
Briefly, we follow the following procedure:
\begin{enumerate}
\item For each of $X$ replicates:
	\begin{enumerate}
		\item partition the allele frequency data into a 90\% ``training'' partition ($F^x_1$) and a 10 \%``testing" partition ($F^x_2$) \label{partition}
		\item run our inference procedure on the training partition to estimate model parameters $\theta_{mk}$ for: \label{inference}
			\begin{enumerate}
				\item $m$: the spatial and the nonspatial model
				\item $k$: the number of clusters 1 through $K$
			\end{enumerate}	
	\item calculate the mean log likelihood of the testing data partition, 
	over the posterior distribution of training-estimated parameters for each model 
	($\bar{\mathcal{L}}(F^x_2 \mid \theta_{mk})$, henceforth $\bar{\mathcal{L}}_{xmk}$) \label{lnL}
	\item generate standardized mean log likelihoods, $\mathcal{Z}_{xmk}$, across models: \label{standardize}
		\begin{enumerate}
			\item identify the highest mean log likelihood, $\bar{\mathcal{L}}^\text{max}_{xmk}$
			\item subtract $\bar{\mathcal{L}}^\text{max}_{xmk}$ from $\bar{\mathcal{L}}_{xmk}$ across all models,
				such that the standardized log likelihood, $\mathcal{Z}_{xmk}$, of the best model is 0,
				and less than 0 for all inferior models. 
		\end{enumerate}
	\end{enumerate}
\item For each model (i.e., each combination of $m$ and $k$) calculate 
	the mean ($	\bar{\mathcal{Z}}_{mk} $) standardized log likelihood of the testing data partition across $X$ replicates, 
	as well its standard error ($SE_{\bar{\mathcal{Z}}_{mk}}$) and
        95\% confidence interval ($\bar{\mathcal{Z}}_{mk} \pm 1.96 \times SE_{\bar{\mathcal{Z}}_{mk}}$).
% 	\begin{enumerate}
% 	\item mean
% 		\begin{equation}
% 			\bar{\mathcal{Z}}_{mk} = \frac{1}{X}\sum\limits_{x=1}^{X}\mathcal{Z}_{xmk}
% 		\end{equation}
% 	\item standard error
% 		\begin{equation}
% 			SE_{\bar{\mathcal{Z}}_{mk}} = \sqrt{\frac{\sum\limits_{x=1}^{X} \left[ {\mathcal{Z}_{xmk} - \bar{\mathcal{Z}}_{mk}} \right]}{X}}
% 		\end{equation}
% 	\item 95\% confidence interval
% 		\begin{equation}
% 			95\% \text{CI} = \bar{\mathcal{Z}}_{mk} \pm 1.96 \times SE_{\bar{\mathcal{Z}}_{mk}}
% 		\end{equation}
% 	\end{enumerate}
% \end{enumerate}

\newpage
\section{Calculating layer \gc{contributions}}\label{layer_importance}
First, we describe the allelic covariance between two samples, $i$, and $j$.
Note that this is the allelic covariance described in Eqn \eqref{allelic_covariance},
in which we randomly polarize alleles,
and not the genetic covariance, which subtracts mean allele frequencies.
Let $A$ and $B$ be a randomly chosen alleles from the two samples, respectively,
at a randomly chosen locus 
(if the two populations are the same, then choose without replacement).
Then, if we let $X=2(A-1/2)$ and $Y=2(B-1/2)$,
since $X$ and $Y$ take the values $\pm 1$,
and thanks to the random polarization, $\E[A] = \E[A] = 1/2$,
$$\begin{aligned}
\E[XY]
        &= \P\{ X=Y \} - \P\{ X \neq Y \} \\
        &= 2 \P\{ X=Y \} - 1 \\
        &= 1 - 2 \P\{ X \neq Y \} .
\end{aligned}$$
To translate, $\P\{ X=Y \}$ is the probability that the alleles from our two focal samples agree with each other,
while $\P\{ X \neq Y \}$ is the probability that they disagree.
For the first thing to happen, $i$ and $j$ must coalesce before coalescing with the reference samples,
so for $X$ and $Y$ to agree they must be more closely related than typical in the population.
The last part, $\P\{ XY \neq 0\}$, is the probability that both samples disagree from the references.
(This implies that $\E[XY] = 1 - 2 D_{ij}$, 
where $D_{ij}$ is the probability that two randomly chosen alleles differ, 
which is the genetic divergence.)

Now, here is a generative model that gives us the form of the covariance we have postulated.
To decide whether or not $X$ and $Y$ will agree,
first each sample randomly chooses a layer: call these $I$ and $J$.
The probability that $X$ chooses layer $k$ is \gc{$\P({I=k})$}, which is $w_i^{(k)}$, 
the $i$th sample's admixture proportion in the $k$th layer.
The same holds true for $Y$.
If they do not choose the same layer, the probability that they agree is $p_\gamma$.
If they do choose the same layer, 
then they agree with a probability $p_\gamma + q^{(k)}_{ij}$ that depends on their distance apart.
Here

@@

One way to summarize the contribution of each layer is to partition the probability of agreement
into contributions due to agreement ``in" each layer.
So, the contribution from layer $k$ to agreement between $i$ and $j$ is 
$w_i^{(k)} w_j^{(k)} q^{(k)}_{ij} / (p_\gamma + \sum_K w_i^{(k)} w_j^{(k)} q^{(k)}_{ij})$,
which is the probability, given that they agree, that they agree thanks to layer $k$.
Similarly, the ``background" contribution is $p_\gamma / (p_\gamma + \sum_K w_i^{(k)} w_j^{(k)} q^{(k)}_{ij})$.
Because our signal comes from \emph{variation} in covariance, we omit
the $p_\gamma$ terms. \gc{Stated in this way this quantity is the
relative contribution of the $k$th layer to the (model-based) kinship
coefficient between $i$ and $j$.}

@@

%
\begin{equation}
\xi^{(k)} = 
	\sum\limits_{i=1}^{N-1}
		\sum\limits_{j=i+1}^N
			w^{(k)}_iw^{(k)}_j 
				\left(	
					2\alpha^{(k)}_0 
						\left( \text{exp} 
							\left( -(\alpha^{(k)}_D D_{i,j}) ^ {\alpha^{(k)}_2}\right) 
						\right) + 2\phi^{(k)} + \frac{1}{2}
				\right)
\label{layer_contribution}
\end{equation}
%
which is that layer's contribution to agreement between samples 
summed over the upper triangle (excluding the diagonal) of the covariance matrix.
We define the \gc{contribution} of the $k$th layer, $\Xi^{(k)}$, 
as the relative contribution of the $k$th layer to total agreement:
%
\begin{equation}
\Xi^{(k)} = 
\frac{\xi^{(k)}}
	{\sum\limits_{k=1}^{K}
	    	\xi^{(k)}}
\label{rel_layer_contribution}
\end{equation}
%
